---
title: "Course-Project-2"
author: "redson"
date: "2023-10-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
SCC <- readRDS("Source_Classification_Code.rds")
```


```{r}
NEI<- readRDS("summarySCC_PM25.rds")
```

```{r}
head(SCC, 10)
```

```{r}
head(NEI, 10)
```


#total emissions from PM2.5 decreased in the United States from 1999 to 2008
```{r}
# Filter data for PM2.5 emissions and years 1999, 2002, 2005, and 2008
data <- subset(NEI, Pollutant == "PM25-PRI" & year %in% c(1999, 2002, 2005, 2008))

# Calculate total emissions for each year
total_emissions <- aggregate(Emissions ~ year, data=data, sum)
```

```{r}
# Create a bar plot
barplot(total_emissions$Emissions, names.arg=total_emissions$year, 
        xlab="Year", ylab="Total PM2.5 Emissions", 
        main="Total PM2.5 Emissions in the United States (1999-2008)")
```
#total emissions from PM2.5 decreased in Baltimore City, Maryland (fips == "24510") from 1999 to 2008?

```{r}
# Filter data for PM2.5 emissions in Baltimore City and years 1999-2008
baltimore_pm25_data <- subset(NEI, Pollutant == "PM25-PRI" & fips == "24510" & year %in% c(1999, 2008))

# Calculate total emissions for each year
total_emissions_baltimore <- aggregate(Emissions ~ year, data=baltimore_pm25_data, sum)

# Create a bar plot
barplot(total_emissions_baltimore$Emissions, names.arg=total_emissions_baltimore$year, 
        xlab="Year", ylab="Total PM2.5 Emissions", 
        main="Total PM2.5 Emissions in Baltimore City (1999-2008)")
```
#four types of sources have seen decreases or increases in emissions in Baltimore City from 1999–2008?
```{r}
install.packages("ggplot2")
library(ggplot2)

# Filter data for Baltimore City and years 1999-2008
baltimore_data <- subset(NEI, fips == "24510" & year %in% c(1999, 2008))

# Create a ggplot2 plot to compare emissions by source type
ggplot(baltimore_data, aes(x=year, y=Emissions, fill=type)) +
  geom_bar(stat="identity") +
  labs(x="Year", y="Emissions", 
       title="Emissions by Source Type in Baltimore City (1999-2008)") +
  scale_fill_discrete(name="Source Type") +
  facet_wrap(~ type, scales="free_y") +
  theme_minimal()
```
#How have emissions from coal combustion-related sources changed across the United States from 1999–2008?

```{r}
# Coal-related SCC
SCC.coal = SCC[grepl("coal", SCC$Short.Name, ignore.case = TRUE), ]

# Merges two data sets
merge <- merge(x = ig, y = SCC.coal, by = 'SCC')
merge.sum <- aggregate(merge[, 'Emissions'], by = list(merge$year), sum)
colnames(merge.sum) <- c('Year', 'Emissions')

```


```{r}
# Coal-related SCC
SCC.coal <- SCC[grepl("coal", SCC$Short.Name, ignore.case = TRUE), ]

# Merges two data sets
merge <- merge(x = NEI, y = SCC.coal, by = 'SCC')
merge.sum <- aggregate(merge[, 'Emissions'], by = list(merge$year), sum)
colnames(merge.sum) <- c('Year', 'Emissions')

ggplot(data = merge.sum, aes(x = Year, y = Emissions / 1000)) + geom_line(aes(group = 1, col = Emissions)) + geom_point(aes(size = 2, col = Emissions)) + ggtitle(expression('Total Emissions of PM'[2.5])) + ylab(expression(paste('PM', ''[2.5], ' in kilotons'))) + geom_text(aes(label = round(Emissions / 1000, digits = 2), size = 2, hjust = 1.5, vjust = 1.5)) + theme(legend.position = 'none') + scale_colour_gradient(low = 'black', high = 'red')
```


#How have emissions from motor vehicle sources changed in Baltimore City and Los Angeles County, California from 1999–2008?
```{r}
# Filter data for motor vehicle sources and years 1999-2008 in Baltimore City
baltimore_motor_data <- subset(NEI, type == "onroad" & fips == "24510" & year %in% c(1999, 2008))

# Filter data for motor vehicle sources and years 1999-2008 in Los Angeles County
la_motor_data <- subset(NEI, type == "onroad" & fips == "06037" & year %in% c(1999, 2008))

# Create a ggplot2 plot to compare motor vehicle emissions in both locations
ggplot() +
  geom_bar(data = rbind(baltimore_motor_data, la_motor_data), 
           aes(x = year, y = Emissions, fill = fips), 
           position = "dodge", stat = "identity", width = 0.4) +
  labs(x = "Year", y = "Emissions", 
       title = "Motor Vehicle Emissions Comparison (1999-2008)") + 
       scale_fill_discrete(name = "Location") +
  facet_grid(year ~ Emissions, scales = "free")
  theme_minimal()
```

